---
title: "Automated Identification and Quatification Pipeline"
#output: html_notebook
---
#Loading the R packages
```{r}
rm(list = ls())

Sys.setenv(JAVA_HOME='C:\\Program Files\\Java\\jdk-11.0.2')
Sys.setenv(R_ZIPCMD = "C:\\Program Files\\WinRAR\\WinRAR.exe")
#devtools::install_github("awalker89/openxlsx")

packagepath <- 'D:/Programming/R/Rpackages/'


install1 <- function(packages){
  new.packages <- packages[!(packages %in% installed.packages()[, "Package"])]
  if (length(new.packages)) 
    install.packages(new.packages,dependencies=TRUE,destdir=packagepath)
  sapply(packages, require, character.only = TRUE)
}
wants1 <- c('XML','flux','qdapRegex','stringi','RMySQL',
           'baseline','OrgMassSpecR','openxlsx','XLConnect','rJava',
           'htmlwidgets','rgl','Rpdb','devtools','zip')
install1(wants1)


install2 <- function(packages) {
  new.packages <- packages[!(packages %in% installed.packages()[, "Package"])]
  if (length(new.packages)) 
    biocLite(new.packages,dependencies=TRUE,destdir=packagepath)
    #BiocManager::install(new.packages,dependencies=TRUE,site_repository=packagepath,update=T,destdir=packagepath)
  sapply(packages, require, character.only = TRUE)  
}
wants2 <- c('MSnbase','Biobase','tibble',
            'xcms','mzR','msdata','faahKO',
            'fpc','MSeasy','baseline','RMassBank','flux','ChemmineR')
#source("https://bioconductor.org/biocLite.R")
BiocManager::install(wants2)
#install2(wants2)


#install_version("XLConnect", version = "0.2-12", repos = "http://cran.us.r-project.org")
#install_version("XLConnectJars", version = "0.2-12", repos = "http://cran.us.r-project.org")


#install.packages('D://Programming/R/Packages/faahKO_1.16.0.tar.gz', repos = NULL, type="source")
#install.packages('D://Programming/R/Packages//ChemmineR_2.28.3.zip', repos = NULL, type="source")
#install.packages('D://Programming/R/Packages/XLConnectJars_0.2-12.tar.gz', repos = NULL, type="source")

```


#Input the folders' name
```{r}
local1 <- 'D:/Career_13_Instrument/004PyGCMS/'
local2 <- paste(local1,'02Rawdata/UNCG_watershed_20220419/',sep="") # Input the folder's name

NISTlib <- paste(local1,'01Others/01MSP_NIST_MS_Library/',sep="")
path01  <- paste(local2,'02CSV/',sep="")
path02  <- 'C:/NISTDEMO/MSSEARCH/'
path03  <- paste(local2,'03NISTSearch/',sep="")
path04  <- paste(local2,'04Chem1/',sep="")
path05  <- paste(local2,'05Chem2/',sep="")
path06  <- paste(local2,'06Check/',sep="")
path07  <- paste(local2,'07Structures/',sep="")
path08  <- paste(local2,'08Output/',sep="")


if (!dir.exists(path03))  {dir.create(path03)}
if (!dir.exists(path04))  {dir.create(path04)}
if (!dir.exists(path05))  {dir.create(path05)}
if (!dir.exists(path06))  {dir.create(path06)}
if (!dir.exists(path07))  {dir.create(path07)}
if (!dir.exists(path08))  {dir.create(path08)}


except <- c('except','has','wants',
            'local1','local2',
            'path01','path02','path03','path04','path05','path06','path07','path08',
            'NISTlib')
```


#(1) Process MS file (.csv) by searching NIST MS library
```{r}
rm(list= ls()[!(ls() %in% except)])
source(paste(local1,"03Rscript/functions.R",sep=''))

filenames <- list.files(path=path01,pattern = '.csv')
#filenames <- filenames[!(filenames %in% list.files(path=path03,pattern = '.csv'))]

for (i in 1:length(filenames)) {
  a1 <- paste(path01,filenames[i],sep=''); a2 <- read.csv(a1,header=F,sep=',',stringsAsFactors=F)
  
  
  # peak identification
  p <- PeakIdentify(a2); p1 <- p$p1; p2 <- p$p2; p3 <- p$p3
  
  
  # plot
  tiff(filename=paste(path03,gsub('.csv','.tif',filenames[i]),sep="/"),compression='lzw',
       width=12,height=8,units='in',res=300,pointsize=22)
  par(mfrow=c(2,1),mar=c(0,0,0.5,0)+0.5,oma=c(2,2,0,0)+0.1)
  plot(as.numeric(p1$time),p1$abundance,type='l',col='black',xaxt='n')
  lines(as.numeric(p1$time),p1$baseline,type='l',col='red')
  #lines(as.numeric(p1$time),p1$baseline*3,type='l',col='red')
  text(max(as.numeric(p1$time))*0.4,max(p1$abundance)*0.9,pos=4,labels="(a) Original spectrum")
  
  plot(as.numeric(p1$time),p1$corrected,type='l',col='black')
  lines(as.numeric(p1$time),matrix(0,nrow=nrow(p1),ncol=1),type='l',col='red')
  lines(as.numeric(p1$time),matrix(mean(p1$corrected)*3,nrow=nrow(p1),ncol=1),type='l',col='blue')
  points(as.numeric(p3$time),p3$corrected,col='red',pch=20,cex=.2)
  text(max(as.numeric(p1$time))*0.4,max(p1$corrected)*0.9,pos=4,
       labels=paste("(b) Baseline corrected spectrum (",nrow(p3),")",sep=''))
  dev.off()
  
  
  # NIST Search
  numofchem <- 20
  ot1 <- as.data.frame(matrix(nrow=0,ncol=11))
  for (j in (1:nrow(p3))) {
    idx <- as.numeric(rownames(p3)[j]) + 1
    b1 <- a2[idx,]
    
    d <- data.frame(t(rbind(a2[1,4:ncol(a2)],b1[1,4:ncol(a2)])))
    if (sum(d[,2])!=0) {
      rownames(d) <- NULL
      d <- cbind('spectrum a',d)
      #plot(d,type='l')
      colnames(d) <- c('filename','mz','intensity')
      metadata <- data.frame(filename = c("Spectrum A"),
                             compound = c("Compound A"))
      WriteMspFile(spectra=d,metadata=metadata,filename=paste(path02,"library.msp",sep=''),comment="")
      m <- SearchNIST2(path02)
      m <- m[1:numofchem,]
    } else {
      m <- matrix(NA,nrow=numofchem,ncol=10) 
    }
    n <- data.frame(cbind(rep(p3[j,]$time,times=nrow(m)),m),stringsAsFactors=F)
    colnames(n) <- c('RetentionTime','Hit','chem','formula','MF','RMF','Prob','CAS','MW','Lib','ID')
    n[,1] <- as.numeric(as.character(n[,1]))
    ot1 <- rbind(ot1,n)

    #n <- t(m)
    #p3[j,(ncol(p1)+1):(ncol(p3)-3)] <- n
    print(paste('NIST Search: ',j,'/',nrow(p3),'/',i,'/',length(filenames),sep=''))
  }
  
  write.csv(ot1,paste(path03,filenames[i],sep=''),row.names=FALSE)
  
}
```


#(2) Process MS file (.csv) by peak quantification - using highest similarity in seletcting compounds
```{r}
rm(list= ls()[!(ls() %in% except)])
source(paste(local1,"03Rscript/functions.R",sep=''))

filenames <- list.files(path=path01)

for (i in 1:length(filenames)) {
  a1 <- paste(path01,filenames[i],sep=''); a2 <- read.csv(a1,header=F,sep=',',stringsAsFactors=F)
  
  
  # peak identification
  p <- PeakIdentify(a2); p1 <- p$p1; p2 <- p$p2; p3 <- p$p3
  
  
  # Chemical at each peak
  b1 <- paste(path03,filenames[i],sep='')
  b2 <- read.csv(b1,header=T,stringsAsFactors=F)
  addcol <- t(colnames(b2)[2:ncol(b2)])
  p3[,addcol] <- NA
  for (j in 1:nrow(p3)) {
    c1 <- b2[which(b2$RetentionTime==as.numeric(p3[j,]$time)),]
    if (!is.integer0(which(!is.na(c1$Hit)))) {
      p3[j,(ncol(p3)-length(addcol)+1):(ncol(p3))] <- c1[which(c1$Hit=='Hit 1'),2:ncol(c1)]
    }
  }

  write.csv(p3, paste(path04,filenames[i],sep=''))
  print(paste('Peak Chem: ',i,'/',length(filenames),sep=''))
}


# Retention Time
RTSummary(local2,path04,path08,'chem1')
```


#(3) Check the compound lists and MySQL connections
```{r}
rm(list= ls()[!(ls() %in% except)])
source(paste(local1,"03Rscript/functions.R",sep=''))

RTSummary(local2,path04,path08,'chem1')

fdpos <- gregexpr('/',local2)[[1]]
foldername <- substr(local2,fdpos[length(fdpos)-1]+1,fdpos[length(fdpos)]-1)

filenames <- list.files(path=path01)

#dbListConnections(MySQL())
all_cons <- dbListConnections(MySQL()); for(con in all_cons) {dbDisconnect(con)}
con <- dbConnect(MySQL(), user="huanc", password="205090", dbname='dom', host="localhost")

xfln <- paste(local2,foldername,'_compound_list.xlsx',sep='')
complist <- openxlsx::read.xlsx(xlsxFile = xfln,sheet = 'Sheet1', colNames = T, rowNames = F)
complist[duplicated(complist$Compounds),]
check1 <- CheckCompList(complist)
if (sum(check1)!=0) {check1[which(check1[,1]==1 | check1[,2]==1),]}
```


#(4) Process MS file (.csv) by peak quantification - using the compound lists as references in selecting compounds
```{r}
rm(list= ls()[!(ls() %in% except)])
source(paste(local1,"03Rscript/functions.R",sep=''))

fdpos <- gregexpr('/',local2)[[1]]
foldername <- substr(local2,fdpos[length(fdpos)-1]+1,fdpos[length(fdpos)]-1)

filenames <- list.files(path=path01)

#dbListConnections(MySQL())
all_cons <- dbListConnections(MySQL()); for(con in all_cons) {dbDisconnect(con)}
con <- dbConnect(MySQL(), user="huanc", password="205090", dbname='dom', host="localhost")

xfln <- paste(local2,foldername,'_compound_list.xlsx',sep='')
complist <- openxlsx::read.xlsx(xlsxFile = xfln,sheet = 'Sheet1', colNames = T, rowNames = F)
#complist[duplicated(complist$Compounds),]
#check1 <- CheckCompList(complist)
#if (sum(check1)!=0) {check1[which(check1[,1]==1 | check1[,2]==1),]}


file.remove(file.path(path05, list.files(path05)))


for (i in 1:length(filenames)) {
  a1 <- paste(path01,filenames[i],sep=''); a2 <- read.csv(a1,header=F,sep=',',stringsAsFactors=F)
  a3 <- paste(path04,filenames[i],sep=''); a4 <- read.csv(a3,header=T,sep=',',stringsAsFactors=F)

  
  # peak identification
  p <- PeakIdentify(a2); p1 <- p$p1; p2 <- p$p2; p3 <- p$p3
  
  
  # Chemical at each peak
  b1 <- paste(path03,filenames[i],sep='')
  b2 <- read.csv(b1,header=T,stringsAsFactors=F)
  addcol <- cbind(t(colnames(b2)[2:ncol(b2)]),'MajorP','area1','area2')
  p3[,addcol] <- NA
  p3$time <- as.numeric(p3$time)
  for (j in 1:nrow(p3)) {
    c1 <- b2[which(b2$RetentionTime==p3[j,]$time),]
    c2 <- which(complist$rt1<=round(p3[j,]$time,3))
    if (!is.integer0(c2)) {
      idx1 <- c2[length(c2)]
      idx2 <- which(c1$chem==complist[idx1,3])
      idx3 <- which(c1$chem==complist[idx1+1,3])
      #idx4 <- which(c1$chem==complist[idx1-1,3])
      
      #if (p3[j,]$time>45) {
      #  idx5 <- which(c1$Hit=='Hit 1')
      #}
      if (!is.integer0(idx2) & !is.integer0(idx3)) {
        d1 <- complist[idx1+1,1] - round(p3[j,]$time,3)
        d2 <- round(p3[j,]$time,3) - complist[idx1,2]
        if (d2 <= 0) {idx5 <- idx2} else if (d2 > 0 & d1 > d2) {idx5 <- idx2} else {idx5 <- idx3}
      } else if (!is.integer0(idx2)) {
        idx5 <- idx2
      } else if (!is.integer0(idx3)) {
        idx5 <- idx3
      } else {
        idx5 <- which(c1$Hit=='Hit 1')
      }
      
      c3 <- c1[idx5,2:ncol(c1)]
      p3[j,(ncol(p3)-length(addcol)+1):(ncol(p3)-3)] <- c3[1,]
    }
  }

  
  # area integration
  for (j in (1:nrow(p3))) {
    lindex <-hindex <- as.numeric(rownames(p3)[j])
    while(p1[lindex,]$Lpeak==0) {lindex <- lindex - 1; if (lindex == 1) break}
    while(p1[hindex,]$Lpeak==0) {hindex <- hindex + 1; if (hindex == nrow(p1)) break}
    
    if (!is.na(p3[j,]$ID)) {
      mpk <- majorpeaks(con,p3,j)
      p3[j,]$MajorP <- paste(mpk,collapse=",")
      mpk <- mpk[which(mpk<=a2[1,ncol(a2)] & mpk>=a2[1,4])] # mpk should inside m/z range from MS data
      
      if (!identical(mpk, numeric(0))) {
        st <- lindex+1
        en <- hindex+1
        x <- as.matrix(as.numeric(a2[st:en,2]))
        if (length(mpk)>1) {
          y <- as.matrix(rowSums(a2[st:en,as.matrix(which(a2[1,] %in% mpk)),drop=FALSE]))
        } else {
          y <- as.matrix(a2[st:en,as.matrix(which(a2[1,] %in% mpk))])
        }
        p3[j,]$area1 <- auc(x, y, thresh = 0, dens = 100) # {flux}
        #plot(x,y)
        
        cx <- as.matrix(as.numeric(p1[lindex:hindex,]$time))
        cy <- as.matrix(p1[lindex:hindex,]$corrected)
        p3[j,]$area2 <- auc(cx, cy, thresh = 0, dens = 100)
      }
    }
  }
  write.csv(p3, paste(path05,filenames[i],sep=''))
  
  
  # plot
  y <- matrix(0,nrow = nrow(p3),ncol = 1)
  for (j in 1:nrow(p3)) {
    idx <- which(complist$rt1 <= p3[j,]$time & 
                   complist$rt2 >= p3[j,]$time & 
                   complist$Compounds == p3[j,]$chem)
    if (!is.integer0(idx)) {y[j,1] <- 1}
  }
  p4 <- p3[which(y[,1]==1),]
  if(is.null(dev.list()) == F){dev.off()}
  tiff(filename=paste(path06,gsub('.csv','.tif',filenames[i]),sep="/"),compression='lzw',
       width=12,height=8,units='in',res=300,pointsize=22)
  plot(as.numeric(p1$time),p1$corrected,type='l',col='black',xlab='retention time (min)',
       ylab = 'corrected abundance')
  points(as.numeric(p4$time),p4$corrected,col='red',pch=20,cex=.5)
  dev.off()
  
  
  print(paste('Peak Chem: ',i,'/',length(filenames),sep=''))
}


dbDisconnect(con)


# Retention Time
RTSummary(local2,path05,path08,'chem2')

```


#(5) Comparision between compounds by two selecting methods - highest similarity VS (highest similarity and previous
# compound lists as references)
#'_output1.xlsx' and '_output2.xlsx'
```{r}
rm(list= ls()[!(ls() %in% except)])
source(paste(local1,"03Rscript/functions.R",sep=''))

fdpos <- gregexpr('/',local2)[[1]]
foldername <- substr(local2,fdpos[length(fdpos)-1]+1,fdpos[length(fdpos)]-1)
filenames <- list.files(path=path05,pattern='.csv')

o1 <- openxlsx::read.xlsx(xlsxFile = paste(path08,foldername,'_rt_chem1.xlsx',sep=''),sheet = 'rt2')
o2 <- openxlsx::read.xlsx(xlsxFile = paste(path08,foldername,'_rt_chem2.xlsx',sep=''),sheet = 'rt2')
o3 <- merge(o1[,1:6],o2[,1:6],by='rt',all.x = T)
o3$top <- NA

xfln <- paste(local2,foldername,'_compound_list.xlsx',sep='')
complist <- openxlsx::read.xlsx(xlsxFile = xfln,sheet = 'Sheet1', colNames = T, rowNames = F)
cmplst <- complist
cmplst[,filenames] <- NA
for (i in 1:length(filenames)) {
  a1 <- filenames[i]
  a2 <- read.csv(paste(path05,a1,sep=''),header=T,stringsAsFactors = F)
  a2 <- a2[!is.na(a2$chem),]
  a3 <- a2[order(-a2$area2),]
  a4 <- a3[1:ceiling(nrow(a3)*0.1),]
  
  idx <- which(o3$rt %in% round(a4$time,3))
  o3[idx,]$top <- 'y'
  
  for (j in 1:nrow(cmplst)) {
    b1 <- sum(a2[which(round(a2$time,3)>=cmplst[j,]$rt1 & 
                         round(a2$time,3)<=cmplst[j,]$rt2 & 
                         a2$chem == cmplst[j,]$Compounds),]$area1)
    if (!is.na(b1)) {b2 <- b1} else {b2 <- 0}
    
    cmplst[j,i+ncol(complist)] <- b2
  }
}
y <- as.data.frame(rowSums(cmplst[,(ncol(complist)+1):ncol(cmplst)] == 0))
cmplst2 <- cmplst[which(y != (ncol(cmplst) - ncol(complist))),]
for (i in (ncol(complist)+1):ncol(cmplst2)) {if (sum(cmplst2[,i])!=0) {cmplst[,i] <- cmplst[,i]/sum(cmplst[,i])*100}}

####
xlsxfln1 <- paste(path08,foldername,'_compound_list.xlsx',sep='')
if (file.exists(xlsxfln1)) {file.remove(xlsxfln1)}
if (nrow(cmplst2) != nrow(cmplst)) {
  complist2 <- merge(complist,cmplst2,by=c('rt1','rt2','Compounds'),all.y = T,sort = F)
  complist2 <- complist2[,1:3]
  # {openxlsx}
  wb <- openxlsx::createWorkbook()
  openxlsx::addWorksheet(wb, "Sheet1")
  openxlsx::writeData(wb, sheet = "Sheet1", complist2, colNames = TRUE)
  openxlsx::setColWidths(wb, sheet = 'Sheet1', cols = 1:ncol(complist2), widths = "auto")
  openxlsx::saveWorkbook(wb, xlsxfln1, overwrite = TRUE)
}


####
# {openxlsx}
wb <- openxlsx::createWorkbook()
openxlsx::addWorksheet(wb, "chem1")
openxlsx::writeData(wb, sheet = "chem1", o3, colNames = TRUE)
openxlsx::saveWorkbook(wb, paste(path08,foldername,'_output1.xlsx',sep=''), overwrite = TRUE)

# {XLConnect}
wb <- XLConnect::loadWorkbook(paste(path08,foldername,'_output1.xlsx',sep=''),create=F)

cs1 <- XLConnect::createCellStyle(wb)
XLConnect::setFillBackgroundColor(cs1, color = XLC$"COLOR.GREY_25_PERCENT")
XLConnect::setFillForegroundColor(cs1, color = XLC$"COLOR.GREY_25_PERCENT")
XLConnect::setFillPattern(cs1, fill = XLC$"FILL.SPARSE_DOTS")

cs2 <- XLConnect::createCellStyle(wb)
XLConnect::setFillBackgroundColor(cs2, color = XLC$"COLOR.GREY_40_PERCENT")
XLConnect::setFillForegroundColor(cs2, color = XLC$"COLOR.GREY_40_PERCENT")
XLConnect::setFillPattern(cs2, fill = XLC$"FILL.SPARSE_DOTS")
XLConnect::setColumnWidth(wb, sheet = "chem1", column = c(3,8), width = 10000)

for (i in 1:nrow(cmplst2)) {
  rt1 <- which(o3$rt>=cmplst2[i,1]); rt2 <- which(o3$rt<=cmplst2[i,2])
  st <- rt1[1] + 1
  en <- rt2[length(rt2)] + 1
  if (i %% 2 == 1) {cellst <- cs1} else {cellst <- cs2}
  for (j in st:en) {XLConnect::setCellStyle(wb,sheet="chem1",row=j,col=1:ncol(o3),cellstyle=cellst)}
}

XLConnect::saveWorkbook(wb)


####
# {openxlsx}
wb <- openxlsx::createWorkbook()
openxlsx::addWorksheet(wb, "chem1")
openxlsx::writeData(wb, sheet = "chem1", cmplst2, colNames = TRUE)
openxlsx::saveWorkbook(wb, paste(path08,foldername,'_output2.xlsx',sep=''), overwrite = TRUE)


```


#(6) Combine Identified Chemicals & Check peak identified or unidentified 
#'_ms.txt'
```{r}
rm(list= ls()[!(ls() %in% except)])
source(paste(local1,"03Rscript/functions.R",sep=''))

fdpos <- gregexpr('/',local2)[[1]]
foldername <- substr(local2,fdpos[length(fdpos)-1]+1,fdpos[length(fdpos)]-1)
filenames <- list.files(path=path05,pattern='.csv')

xlsxfln1 <- paste(path08,foldername,'_compound_list.xlsx',sep='')
xlsxfln2 <- paste(local2,foldername,'_compound_list.xlsx',sep='')
if (file.exists(xlsxfln1)) {xfln <- xlsxfln1} else {xfln <- xlsxfln2}
complist <- openxlsx::read.xlsx(xlsxFile = xfln,sheet = 'Sheet1',colNames = T,rowNames = F)


file.remove(file.path(path06, list.files(path06,pattern='.csv')))


ot1 <- as.data.frame(matrix(nrow=0,ncol=20))
for (i in 1:length(filenames)) {
  a1 <- filenames[i]
  a2 <- read.csv(paste(path05,a1,sep=''),header=T,stringsAsFactors = F)
  a2[,'Identified'] <- 0 # 0 - Unidentified, 1 - Identified
  
  for (j in 1:nrow(a2)) {
    b1 <- which(complist$rt1<=round(a2[j,]$time,3))
    if (!is.integer0(b1)) {
      b2 <- b1[length(b1)]
      if (complist[b2,]$rt2 >= round(a2[j,]$time,3) & complist[b2,]$Compounds==a2[j,]$chem) {
        a2[j,]$Identified <- 1
        }
    }
  }
  write.csv(a2, paste(path06,a1,sep=''))
  
  
  ot2 <- as.data.frame(matrix(nrow=nrow(a2),ncol=20))
  colnames(ot1) <- colnames(ot2) <- c('filename',colnames(a2)[c(2:5,9:22)],'areaPer')
  ot2[,1] <- a1
  ot2[,2:19] <- a2[,c(2:5,9:22)]
  ot2[which(ot2$Identified==1),]$areaPer <- 
    ot2[which(ot2$Identified==1),]$area1/sum(ot2[which(ot2$Identified==1),]$area1)*100
  ot1 <- rbind(ot1,ot2)
  
  print(paste('Finished: ',i,'/',length(filenames),'/',nrow(ot2),sep=''))
}
write.table(ot1,paste(path08,foldername,'_ms.txt',sep=''),sep="\t",row.names=FALSE)
```


#(7) Classification of organics
# '*_output3.xlsx'
```{r}
rm(list= ls()[!(ls() %in% except)])
source(paste(local1,"03Rscript/functions.R",sep=''))

fdpos <- gregexpr('/',local2)[[1]]
foldername <- substr(local2,fdpos[length(fdpos)-1]+1,fdpos[length(fdpos)]-1)
raw01 <- read.table(paste(path08,foldername,'_ms.txt',sep=''),header=T,stringsAsFactors=F)
pahlist <- openxlsx::read.xlsx(xlsxFile = paste(local1,'02Rawdata/PAH_list.xlsx',sep=''),sheet = 'Sheet1',colNames = T)

xlsxfln1 <- paste(path08,foldername,'_compound_list.xlsx',sep='')
xlsxfln2 <- paste(local2,foldername,'_compound_list.xlsx',sep='')
if (file.exists(xlsxfln1)) {xfln <- xlsxfln1} else {xfln <- xlsxfln2}
complist <- openxlsx::read.xlsx(xlsxFile = xfln,sheet = 'Sheet1',colNames = T,rowNames = F)

####
all_cons <- dbListConnections(MySQL()); for(con in all_cons) {dbDisconnect(con)}
con <- dbConnect(MySQL(), user="huanc", password="205090", dbname='dom', host="localhost")
col <- fetch(dbSendQuery(con,"select column_name from information_schema.columns where table_name='raw01NIST' ORDER BY ordinal_position"))
####
raw02 <- raw01[which(raw01$Identified==1),]
chem01 <- raw02[!duplicated(raw02[,which(colnames(raw02) %in% c('Lib','ID'))]),c(7:10,12:16)]

st <- 34; en <- 108
addindex1 <- c(as.character(col[st:en,1]))
chem02 <- as.data.frame(matrix(0,nrow=nrow(chem01),ncol=length(addindex1)))
struc <- as.data.frame(matrix(0,nrow=nrow(chem01),ncol=nrow(col)))
colnames(chem02) <- addindex1
colnames(struc) <- as.character(t(col))
for (i in 1:nrow(chem01)) {
  s0 <- trimws(gsub('>>','',gsub('<<','',chem01[i,]$Lib)))
  s1 <- chem01[i,]$ID
  sqlquery <- paste("select * from raw01NIST where DB=",s1," and library='",s0,"';",sep='')
  sq1 <- dbSendQuery(con, sqlquery)
  s2 <- fetch(sq1)
  
  struc[i,] <- s2
  chem02[i,1:(en-st+1)] <- s2[,c(st:en)]
  if (floor(i/100)==i/100) {print(paste(i,'/',nrow(chem01),sep=''))}
}
dbDisconnect(con)
chem03 <- cbind(chem01,chem02)
struc <- cbind(chem01,struc)
####
elemt <- c("H","C","N","O","S","P")
chain <- c("RNH2","R2NH","R3N",
           "ROPO3","ROH","RCHO","RCOR","RCOOH","RCOOR","ROR",
           "RCCH","RCN",
           "RINGS","AROMATIC")
funcg <- c('SaH','UnSaH','ArH','PAH','Carb','PhC','LgC','Ntg')
####
colnames(chem03)
idx1 <- which(colnames(chem03) %in% elemt | colnames(chem03) %in% chain)
chem04 <- chem03[,c(1:9,idx1)]

##
chem04[,funcg] <- 0
for (i in 1:nrow(chem04)) {
  a1 <- chem03[i,10:ncol(chem03)]
  #colnames(a1)
  
  if (a1$C!=0 & a1$H!=0 & sum(a1[,c(3:29,44:75)])==0) { # hydrocarbon
    if (trimws(chem04[i,]$CAS) %in% pahlist$CAS) {
      chem04[i,]$PAH <- 1
    } else if (a1$AROMATIC !=0) {
      if (a1$AROMATIC==1) {chem04[i,]$ArH <- 1} else {chem04[i,]$PAH <- 1}
    } else if (a1$C*2+2==a1$H | a1$C*2+2==a1$H+a1$RINGS*2) {
      chem04[i,]$SaH <- 1
    } else {
      chem04[i,]$UnSaH <- 1
    } 
  } else if (a1$C!=0 & a1$H!=0 & a1$O!=0 & sum(a1[,c(3,5:29,44:75)])==0) { # carbohydrate
    if (a1$AROMATIC!=0 & a1$ROH!=0 & a1$ROR!=0) {
      chem04[i,]$LgC <- 1
    } else if (a1$AROMATIC!=0 & a1$ROH!=0) {
      chem04[i,]$PhC <- 1
    } else {chem04[i,]$Carb <- 1}
  }
  #if (a1$Cl!=0 | a1$F!=0 | a1$Br!=0) {chem04[i,]$Hal <- 1}
  if (a1$N !=0) {chem04[i,]$Ntg <- 1}
  
  if (grepl('naphthalene', tolower(chem03[i,]$chem)) & chem04[i,]$ArH == 1) {
    chem04[i,]$ArH <- 0
    chem04[i,]$PAH <- 1
  }
}
# {openxlsx}
wb <- openxlsx::createWorkbook()
openxlsx::addWorksheet(wb, "Uniquechem")
openxlsx::writeData(wb, sheet = "Uniquechem", chem04, colNames = TRUE)
openxlsx::setColWidths(wb, sheet = 'Uniquechem', cols = 1:ncol(chem04), widths = "auto")
openxlsx::saveWorkbook(wb, paste(path08,foldername,'_output3.xlsx',sep=''), overwrite = TRUE)
####
y <- matrix(0,nrow = nrow(complist), ncol = 1)
for (i in 1:nrow(complist)) {
  idx <- which(chem04$chem == complist[i,]$Compounds)
  if (!is.integer0(idx)) {y[i,1] <- 1}
}
complist2 <- complist[which(y==1),]
criteria <- nrow(complist2) != nrow(complist) & nrow(complist2 != 0)
criteria <- FALSE
if (criteria) {
  # {openxlsx}
  wb <- openxlsx::createWorkbook()
  openxlsx::addWorksheet(wb, "Sheet1")
  openxlsx::writeData(wb, sheet = "Sheet1", complist2, colNames = TRUE)
  openxlsx::setColWidths(wb, sheet = 'Sheet1', cols = 1:ncol(complist2), widths = "auto")
  openxlsx::saveWorkbook(wb, paste(local2,foldername,'_compound_list.xlsx',sep=''), overwrite = TRUE)
}
####
file.remove(file.path(path07, list.files(path07)))
for (i in 1:nrow(complist2)) {
  idx <- which(struc$chem==complist2[i,]$Compounds)[1]
  
  if (!is.na(idx)) {
    sdfset <- ChemmineR::read.SDFset(paste(NISTlib,'sdf/',struc[idx,]$file.y,sep=''))
    
    posi1 <- gregexpr('_',struc[idx,]$file.y)[[1]][1]
    posi2 <- gregexpr('-',struc[idx,]$file.y)[[1]][1]
    stanum <- as.numeric(substr(struc[idx,]$file.y,posi1+1,posi2-1))
    
    a1 <- struc[idx,]$DB
    #a2 <- as.numeric(substr(a1,nchar(a1)-2,nchar(a1)))
    a2 <- a1 - stanum + 1
    if (identical(struc[idx,]$chem.x,sdfid(sdfset)[a2])) {
      a3 <- sdfset[a2]
      a3@ID <- paste('(c',i,') ',sdfid(sdfset)[a2],sep='')
      #a3@ID <- paste('c',i,sep='')
      
      
      fln <- paste(path07,i,".tif",sep="")
      if(is.null(dev.list()) == F){dev.off()}
      tiff(filename=fln,compression='lzw',width=6,height=6,units='in',res=300,pointsize=22)
      plot(a3, print=F,regenCoords=T)
      dev.off()
      
      print(paste(i,'/',nrow(complist2),' (',a3@ID,')',sep=''))
    }
  }
}
```


#(8) Output the information of products for further analysis
# '*_output4.xlsx'
```{r}
rm(list= ls()[!(ls() %in% except)])
source(paste(local1,"03Rscript/functions.R",sep=''))

fdpos <- gregexpr('/',local2)[[1]]
foldername <- substr(local2,fdpos[length(fdpos)-1]+1,fdpos[length(fdpos)]-1)
raw01 <- read.table(paste(path08,foldername,'_ms.txt',sep=''),header=T,stringsAsFactors=F)
chem04 <- openxlsx::read.xlsx(xlsxFile=paste(path08,foldername,'_output3.xlsx',sep=''),sheet='Uniquechem',colNames=T)

xlsxfln1 <- paste(path08,foldername,'_compound_list.xlsx',sep='')
xlsxfln2 <- paste(local2,foldername,'_compound_list.xlsx',sep='')
if (file.exists(xlsxfln1)) {xfln <- xlsxfln1} else {xfln <- xlsxfln2}
complist <- openxlsx::read.xlsx(xlsxFile = xfln,sheet = 'Sheet1',colNames = T,rowNames = F)

####
funcg <- c('SaH','UnSaH','ArH','PAH','Carb','PhC','LgC','Ntg')
##
t1 <- unique(chem04$chem)
for (i in 1:length(t1)) {
  a1 <- chem04[which(chem04$chem==t1[i]),(ncol(chem04)-length(funcg)+1):ncol(chem04)]
  if (nrow(a1)>1) {if (nrow(a1[!base::duplicated(a1),])!=1) {print('FALSE')}}
}
####
ot01 <- merge(raw01,chem04[,c(7:8,10:ncol(chem04))],by = c('Lib','ID'),all.x = T)
ot01 <- ot01[order(ot01$filename,ot01$time),]
ot01[which(ot01$Identified==0),ncol(raw01):ncol(ot01)] <- NA
####
chem05 <- complist
addIDX <- c(c('formula','CAS','MW'),colnames(chem04)[9:ncol(chem04)],'Groups')
chem05[,addIDX] <- NA
colnames(chem05)
for (i in 1:nrow(chem05)) {
  a1 <- chem04[which(chem04$chem==chem05[i,]$Compounds),][1,]
  chem05[i,]$formula <- a1$formula
  chem05[i,]$CAS <- a1$CAS
  chem05[i,]$MW <- a1$MW
  chem05[i,7:(ncol(chem05)-1)] <- a1[1,9:ncol(chem04)]
  gp <-''
  for (j in 28:(ncol(chem05)-1)) {if (chem05[i,j]==1) {gp <- paste(gp,colnames(chem05)[j],sep=',')}}
  if (substr(gp,1,1)==',') {chem05[i,ncol(chem05)] <- substr(gp,2,nchar(gp))}
}
####
colnames(chem04)
file <- unique(ot01$filename)
ot02 <- as.data.frame(matrix(0,nrow=length(file),ncol=length(funcg)+2))
colnames(ot02) <- c('filename','NumofChem',funcg)
ot03 <- as.data.frame(matrix(0,nrow=length(file),ncol=4))
colnames(ot03) <- c('filename',
                    'NumofIdentifiedPeaks',
                    'NumofUnidentifiedPeaks',
                    'AearPer_IdentifiedPeaks')
ot02[,1] <- ot03[,1] <- file
for (i in 1:length(file)) {
  a1 <- ot01[which(ot01$filename==ot02[i,]$filename & ot01$Identified==1),]
  a2 <- a1[,(ncol(ot01)-length(funcg)+1):ncol(ot01)]
  ot02[i,2] <- length(unique(a1$chem))
  for (j in 1:ncol(a2)) {if (sum(a2[,j])!=0) {ot02[i,ncol(ot02)-length(funcg)+j] <- sum(a1[which(a2[,j]!=0),]$areaPer)}}
  
  b1 <- ot01[which(ot01$filename==ot03[i,]$filename),]
  if (!is.integer0(which(b1$Identified==1))) {
    ot03[i,2] <- nrow(b1[which(b1$Identified==1),])
  } else {
    ot03[i,2] <- 0
  }
  if (!is.integer0(which(b1$Identified==0))) {
    ot03[i,3] <- nrow(b1[which(b1$Identified==0),])
  } else {
    ot03[i,3] <- 0
  }
  
  ot03[i,4] <- sum(b1[which(b1$Identified==1),]$area2,na.rm=T)/sum(b1$area2,na.rm=T)*100
  
  c1 <- a1[,(which(colnames(ot01)=='areaPer')+1):(ncol(ot01)-length(funcg))]*a1$areaPer/100
}

####
chem02 <- openxlsx::read.xlsx(xlsxFile=paste(path08,foldername,'_output2.xlsx',sep=''),
                              sheet='chem1',colNames=T)
ot05 <- plyr::join(chem05[,c('rt1','rt2','Groups')],chem02,
                   by=c('rt1','rt2'),type='left',match='all')

####
# {openxlsx}
wb <- openxlsx::createWorkbook()

openxlsx::addWorksheet(wb, "chem")
openxlsx::addWorksheet(wb, "CompoundList")
openxlsx::addWorksheet(wb, "product")
openxlsx::addWorksheet(wb, "Classified")
openxlsx::addWorksheet(wb, "Identified")

openxlsx::writeData(wb, sheet = "chem",         ot01,   colNames = TRUE)
openxlsx::writeData(wb, sheet = "CompoundList", chem05, colNames = TRUE)
openxlsx::writeData(wb, sheet = "product",      ot05,   colNames = TRUE)
openxlsx::writeData(wb, sheet = "Classified",   ot02,   colNames = TRUE)
openxlsx::writeData(wb, sheet = "Identified",   ot03,   colNames = TRUE)

openxlsx::setColWidths(wb, sheet = 'Classified', cols = 1:ncol(ot02), widths = "auto")
openxlsx::setColWidths(wb, sheet = 'Identified', cols = 1:ncol(ot03), widths = "auto")

openxlsx::saveWorkbook(wb, paste(path08,foldername,'_output4.xlsx',sep=''), overwrite = TRUE)


unique(chem05$Groups)
```

